### 2015-07-20 text/ms.Rmd
Edits before sending out draft

\noindent
^11^National Marine Fisheries Service, 
National Oceanic and Atmospheric Administration, 
Fisheries Resource Assessment and Monitoring Division, 
Northwest Fisheries Science Center, Seattle, WA, 98112, USA

@@

Whereas averages or weighted averages may improve predictions over any single
model, they may not optimally leverage available data. The truth does not
necessarily lie in the middle of multiple model predictions, some models may
perform better than others in certain conditions, and the covariance between
models may contain information that can improve predictive accuracy. We can
exploit these characteristics by using the predictions from a group of models as
inputs into a separate statistical model. This technique, sometimes called
superensemble modelling [@krishnamurti1999], is common in climate and weather
forecasting [e.g. @yun2005; @mote2015]. The superensemble is fit to some
training dataset where outcomes are well known and used to predict on a dataset
of interest. For example, @krishnamurti1999 combined predictions of wind and
precipitation in Asian monsoons via a superensemble regression fit to observed
data. Their superensemble was considerably more accurate than any individual
prediction or weighted average of predictions.

@@

* *SSCOM* (state-space catch-only model) is a hierarchical model that, similar
  to COM-SIR, is based on a coupled harvest-dynamics model [@thorson2013].
  SSCOM estimates unobserved dynamics in both fishing effort and the fished
  population based on a catch time series and priors on $r$, the maximum rate
  of increase of fishing effort, and the magnitude of various sources of
  stochasticity. The model is fit in a Bayesian state-space framework to
  integrate across three forms of stochasticity: variation in effort,
  population dynamics, and fishing efficiency [@thorson2013].

@@

\noindent 
where $L$ is a generalized loss function, $f$ is some generalized regression
function, $\hat{b}_\mathrm{CMSY}$ is the mean or slope prediction from the CMSY
model etc. (Table \ref{tab:predictors}), $S(0.2)$ and $S(0.05)$ represent the
spectral density of the scaled catch series at frequencies of 0.20 and 0.05, $b$
is the mean or slope value the model is fitted to, and $\theta$ is the set of
parameters for the regression function. For all superensemble models of mean
$B/B_\mathrm{MSY}$---a ratio bounded at zero---we fit the models in log space
and exponentiated the predictions. For the estimates of $B/B_\mathrm{MSY}$
slope, which are not bounded at zero, we fit superensemble models on the natural
untransformed scale.

@@

A critical component to any predictive modelling exercise is to evaluate the
performance of a model on new data [@hastie2009]. We used repeated three-fold
cross validation to test predictive performance: we randomly divided the
dataset into three sets, built superensemble models on two-thirds of the data, and
evaluated predictive performance on the remaining third. We repeated this
across each of the three splits and then repeated the whole procedure 50 times
to account for bias that may result from any one set of validation splits.
Since the dynamics of simulated populations differing only in the stochastic
draw of random values are likely similar, we grouped these stocks (10 per
factorial cell) in the cross-validation process into either the training or
testing split. Since mPRM is built on the RAM Legacy Stock Assessment database,
when testing model performance on the stock assessment database, we refit mPRM
on each training split.

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations [e.g. @walther2005]. Here,
we measure proportional error, defined as
$(\hat{b} - b)/b$, where $\hat{b}$ and $b$ represent estimated and 'true'
(or stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median proportional
error to measure bias, median absolute proportional error to measure accuracy,
and Spearman's rank-order correlation between predicted and 'true' values to
measure the ability to correctly rank populations. Code to reproduce our
analysis is available at
<https://github.com/datalimited/ensembles>.

@@

Applied to the simulated dataset of known status, the individual models had
variable success at recovering the mean (status) and slope (trajectory) of
$B/B_\mathrm{MSY}$ in the last five years. All models exhibited a high degree of scatter
around the 1:1 line of perfect status prediction (Fig. \ref{hexagon}). CMSY
exhibited bimodal predictions of status but had the best rank-order correlation
and accuracy scores (Fig. \ref{performance}a). COM-SIR and SSCOM both correctly
identified a number of low status stocks, but frequently predicted a high
status when status was in fact low (Fig. \ref{hexagon}b, c). mPRM had
relatively poor ability to predict status for the simulated dataset (Fig.
\ref{hexagon}d). There was generally little correlation between true and
predicted trajectory for any of the individual models besides SSCOM (Figs
\ref{scatter-sim-slope}a--d).

Ensemble methods, and in particular the machine learning superensemble models (random
forest and GBM), generally improved estimates of status and trajectory over any individual model (Fig.
\ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h). Compared to the
individual models, machine learning superensembles improved accuracy (median
absolute proportional error) by 
<!--TODO: check these percentage values- right?-->
`r mean_sim$mach_vs_ind_mare_fold`%, 
increased rank-order correlation from `r mean_sim$ind_corr_range` 
to `r mean_sim$mach_corr_range`, 
and reduced bias (median proportional error) from 
`r mean_sim$ind_mre_range` to 
`r mean_sim$mach_mre_range` (Fig. \ref{performance}a). 
These superensembles also had better ability to distinguish if
simulated stocks were above or below $B/B_\mathrm{MSY} = 1$ (Fig.
\ref{roc-sim}). Results were similar when predicting trajectory: compared to
individual models, machine learning superensembles improved accuracy by 
`r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from 
`r slope_sim$ind_corr_range` to 
`r slope_sim$mach_corr_range`, and reduced bias
from `r slope_sim$ind_mre_range` 
to `r slope_sim$mach_mre_range` (Fig. \ref{performance-sim-slope}). The
ensemble models that simply took a mean of the individual models ranked
slightly behind the best individual model for estimating fish stock status (CMSY; Fig.
\ref{performance}a) and had slightly lower correlation but higher accuracy than
the best individual model at predicting the trends of status (SSCOM; Fig.
\ref{performance-sim-slope}).

@@

Ensemble methods provide a useful approach to situations where conservation and
ecological resource management decisions must be made on the basis of multiple,
potentially contrasting estimates of status---a situation common to many
ecological settings beyond fisheries. Compared to individual models of fish
population status, ensemble methods were consistently the best or among the best
across three performance dimensions (accuracy, bias, and rank-order
correlation), two response variables (status and trajectory), two datasets
(simulated and global fisheries), and multiple ensemble methods (from a
simple average to machine learning superensembles). Our results suggest choosing an
superensemble model that allows for non-parametric relationships, such as machine
learning methods. These methods provide added insight into individual model
behaviour and generally performed the best; however, even a simple average of
predictions across multiple models may provide a more useful measure of the
desired parameter than a single model in many cases.

@@

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criterion (AIC) is a
common analytical approach in ecology [@burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble methods
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890]. A
fundamental difference is that coefficient averaging focuses on averaging
*coefficients* whereas ensembles instead average *predictions*. While the
outcome will be the same in some cases, ensembles provide a more general
purpose tool: they do not require information theoretics and they can combine
different types of models (e.g. parametric and non-parametric models or
frequentist and Bayesian predictions). Furthermore, superensembles extend these
benefits by allowing model predictions be combined in via non-linear functions
that are tuned to known data.

@@

As @box1987 noted, all models are wrong, but they may still be useful. The
ensemble methods we investigated attempt to piece together the useful parts of
candidate models to build a model with improved performance. Instead of viewing
the superensemble as a black box, we think considerable mechanistic
understanding can be gained by studying its structure. For example, when SSCOM
estimates very low status this is likely the case, conversely when COMSIR
estimates low status, the truth is likely that the status is high (Fig.
\ref{partial-sim}). These models have two main differences: (1) the form of
effort dynamics and (2) the allowance for both measurement and process error in
SSCOM, whereas the implemented COMSIR admits measurement error only. Were the
methods to differ only in effort dynamics, the results point towards a more
suitable representation of effort dynamics at low biomasses in SSCOM. We think
that such investigation of the parameters of a superensemble may lead to
improvement in the mechanisms imparted to the individual models.

@@

<!--Place the acknowledgment paragraph on the cover page of your manuscript.
(Reviewers are not provided with a cover page.) Do not spell out first (given)
names. Provide the first initial of the first name, even if the initial starts a
sentence. Do not use titles (e.g., Dr. or Professor). Refer to authors of the
manuscript by their initials only (e.g., “S.T.W. was supported by a grant from
the Torry Foundation.”).-->
We thank members of Phase I of the working group 'INSERT NAME HERE' who
contributed to developing the data-limited methods and simulations used in our
analysis.
We thank J.A. Hutchings for helpful discussions on ensemble methods for
assessing population status.
We thank the Gordon and Betty Moore Foundation for funding of the working group
'INSERT NAME HERE'.

>>>>

\noindent
^11^ Fisheries Resource Analysis and Monitoring Division, Northwest Fisheries Science Center, National Marine Fisheries Service, NOAA, Seattle, WA 98112

@@

Whereas averages or weighted averages may improve predictions over any single model, they may not optimally leverage available data. The best prediction does not necessarily lie in the middle of multiple model predictions, some models may perform better than others in certain conditions, and the covariance between models may contain information that can improve predictive accuracy. We can exploit these characteristics by using the predictions from a group of models as inputs into a separate statistical model. This technique, sometimes called superensemble modelling [@krishnamurti1999], is common in climate and weather forecasting [e.g. @yun2005; @mote2015]. The superensemble is fit to some training dataset where outcomes are well known and used to predict on a dataset of interest. For example, @krishnamurti1999 combined predictions of wind and precipitation in Asian monsoons via a superensemble regression fit to observed data. Their superensemble was considerably more accurate than any individual prediction or weighted average of predictions.

@@

* *SSCOM* (state-space catch-only model) is a hierarchical model that, similar to COM-SIR, is based on a coupled harvest-dynamics model [@thorson2013]. SSCOM estimates unobserved dynamics in both fishing effort and the fished population based on a catch time series and priors on $r$, the maximum rate of increase of fishing effort, and the magnitude of various forms of stochasticity. The model is fit in a Bayesian state-space framework to integrate across three forms of stochasticity: variation in effort, population dynamics, and fishing efficiency [@thorson2013].

@@

\noindent 
where $L$ is a generalized loss function, $f$ is some generalized regression function, $\hat{b}_\mathrm{CMSY}$ is the mean or slope prediction from the CMSY model etc.\ (Table \ref{tab:predictors}), $S(0.2)$ and $S(0.05)$ represent the spectral density of the scaled catch series at frequencies of 0.20 and 0.05, $b$ is the mean or slope value the model is fitted to, and $\theta$ is the set of parameters for the regression function. For all superensemble models of mean $B/B_\mathrm{MSY}$---a ratio bounded at zero---we fit the models in log space and exponentiated the predictions. For the estimates of $B/B_\mathrm{MSY}$ slope, which are not bounded at zero, we fit superensemble models on the natural untransformed scale.

@@

A critical component to any predictive modelling exercise is to evaluate the performance of a model on new data [@hastie2009]. We used repeated three-fold cross validation to test predictive performance: we randomly divided the dataset into three sets, built superensemble models on two-thirds of the data, and evaluated predictive performance on the remaining third. We repeated this across each of the three splits and then repeated the whole procedure 50 times to account for bias that may result from any one set of validation splits. Since the dynamics of simulated populations differing only in the stochastic draw of random values are likely similar, we grouped these stocks (10 per factorial cell) in the cross-validation process into either the training or testing split. When applied to the RAM Legacy Stock Assessment database, we used superensembles trained on the entire simulation dataset. However, since mPRM is built on the same stock assessment database, we refit mPRM on each training split.

Predictive performance can be evaluated with metrics that represent a variety of modelling goals. For continuous response variables such as the mean and slope of population status, performance metrics often measure some form of bias, precision, accuracy (a combination of bias and precision), or the ability to correctly rank or correlate across populations [e.g. @walther2005]. Here, we measure proportional error, defined as $(\hat{b} - b)/b$, where $\hat{b}$ and $b$ represent estimated and 'true' (or stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median proportional error to measure bias, median absolute proportional error to measure accuracy, and Spearman's rank-order correlation between predicted and 'true' values to measure the ability to correctly rank populations. We measured the ability for each model to correctly place stocks into categories of above or below $B/B_\mathrm{MSY} = 1$ at any decision threshold by plotting receiver operating characteristic curves. Code to reproduce our analysis is available at <https://github.com/datalimited/ensembles>.

@@

Applied to the simulated dataset of known status, the individual models had variable success at recovering the mean (status) and slope (trajectory) of $B/B_\mathrm{MSY}$ in the last five years. All models exhibited a high degree of scatter around the one-to-one line of perfect status prediction (Fig. \ref{hexagon}). CMSY exhibited bimodal predictions of status but had the best rank-order correlation and accuracy scores (Fig. \ref{performance}a). COM-SIR and SSCOM both correctly identified a number of low status stocks, but frequently predicted a high status when status was in fact low (Fig. \ref{hexagon}b, c). mPRM had relatively poor ability to predict status for the simulated dataset (Fig. \ref{hexagon}d). There was generally little correlation between true and predicted trajectory for any of the individual models (rank-order correlation = `r range_slope_corr_non_sscom`) besides SSCOM (correlation = `r slope_corr_sscom`; Figs \ref{scatter-sim-slope}a--d).

Ensemble methods, and in particular the machine learning superensemble models (random forest and GBM), generally improved estimates of status and trajectory over any individual model (Fig. \ref{hexagon}e--h, Fig. \ref{scatter-sim-slope}e--h). Compared to the individual models, machine learning superensembles improved accuracy (median absolute proportional error) by `r mean_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from `r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and reduced bias (median proportional error) from `r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range` (Fig. \ref{performance}a). These superensembles also had better ability to distinguish if simulated stocks were above or below $B/B_\mathrm{MSY} = 1$ (Fig. \ref{roc-sim}). Results were similar when predicting trajectory: compared to individual models, machine learning superensembles improved accuracy by `r slope_sim$mach_vs_ind_mare_fold`%, increased rank-order correlation from `r slope_sim$ind_corr_range` to `r slope_sim$mach_corr_range`, and reduced bias from `r slope_sim$ind_mre_range` to `r slope_sim$mach_mre_range` (Fig. \ref{performance-sim-slope}). The ensemble models that simply took a mean of the individual models ranked slightly behind the best individual model for estimating fish stock status (CMSY; Fig. \ref{performance}a) and had slightly lower correlation but higher accuracy than the best individual model at predicting the trends of status (SSCOM; Fig. \ref{performance-sim-slope}).

@@

Ensemble methods provide a useful approach to situations where conservation and ecological resource management decisions must be made on the basis of multiple, potentially contrasting estimates of status---a situation common to many settings beyond fisheries. Compared to individual models of fish population status, ensemble methods were consistently the best or among the best across three performance dimensions (accuracy, bias, and rank-order correlation), two response variables (status and trajectory), two datasets (simulated and global fisheries), and multiple ensemble methods (from a simple average to machine learning superensembles). Our results suggest choosing an superensemble model that allows for non-parametric relationships, such as machine learning methods. These methods provide added insight into individual model behaviour and generally performed the best; however, even a simple average of predictions across multiple models may provide a more useful measure of the desired parameter than a single model in many cases.

@@

Multi-model inference in the form of coefficient averaging weighted by information theoretics such as the Akaike Information Criterion (AIC) is a common analytical approach in ecology [@burnham2002; @johnson2004; @grueber2011]. The ensemble methods described in this paper share similarities with coefficient averaging but differ in other important ways. Ensemble methods and coefficient averaging share the long-held notion that multiple working hypotheses can contribute useful information for inference [@chamberlin1890]. A fundamental difference is that coefficient averaging focuses on averaging *coefficients* whereas ensembles instead average *predictions*. While the outcome will be the same in some cases, ensembles provide a more general purpose tool: they do not require information theoretics and they can combine different types of models (e.g. parametric and non-parametric models or frequentist and Bayesian predictions). Furthermore, superensembles extend these benefits by allowing model predictions to be combined via non-linear functions that are tuned to known data.

@@

As @box1987 noted, all models are wrong, but some may still be useful. The ensemble methods we investigated attempt to piece together the useful parts of candidate models to build a model with improved performance. Instead of viewing the superensemble as a black box, we think considerable mechanistic understanding can be gained by studying its structure. For example, when SSCOM estimates very low status this is likely the case, conversely when COMSIR estimates low status, the truth is likely that the status is high (Fig. \ref{partial-sim}). These models have two main differences: (1) the form of effort dynamics and (2) the allowance for both measurement and process error in SSCOM, whereas the implemented COMSIR admits measurement error only. Were the methods to differ only in effort dynamics, the results point towards a more suitable representation of effort dynamics at low biomasses in SSCOM. We think that such investigation of the parameters of a superensemble may lead to improvement in the mechanisms imparted to the individual models.

@@

<!--Place the acknowledgment paragraph on the cover page of your manuscript.
(Reviewers are not provided with a cover page.) Do not spell out first (given)
names. Provide the first initial of the first name, even if the initial starts a
sentence. Do not use titles (e.g., Dr. or Professor). Refer to authors of the
manuscript by their initials only (e.g., “S.T.W. was supported by a grant from
the Torry Foundation.”).-->
We thank members of Phase I of the working group 'INSERT NAME HERE' who
contributed to developing the data-limited methods and simulations used in our
analysis.
We thank J.A. Hutchings for helpful discussions on ensemble methods for
assessing population status.
We thank the Gordon and Betty Moore Foundation for funding of the working group
'INSERT NAME HERE'.
'INSERT OTHER REQUIRED FUNDING ACKNOWLEDGEMENTS HERE'
